\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-02 appendix-1.Rmd
Table abnd figs
Duplicate chunk error fixed

```{r options-appendix, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
set.seed(123)
par(family = "Arial")
```

```{r lib, include=FALSE}

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(car)#revercoding 
library(psych)
library(dlookr)
library(plyr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
library(gt)
library(gtExtras)
library(likert)
library(VIM) #Missing data
library(kutils)
library(simsem)
library(tabledown)
library(Hmisc)
r_refs("references.bib")
```

@@

# Confirming the five factor solution obtained using minimum residual extraction method

```{r MinRes, include=F}
library(psych)
library(tabledown)
library(kableExtra)#without this pdf rendering will not happen

data <- readRDS("leba_2021-09-08.rds")

# Separating EFA and CFA samples with descriptive column
descriptives.data <- data

## Merge "0"s and "1"s into "1"s select,subset assign)
descriptives.data[ , 9:56 ][ descriptives.data[ , 9:56 ] == 0 ] <- 1
#EFA.descriptives <- descriptives.data[1:428,]
EFA.descriptives <- subset(descriptives.data, IncludedInEFA == "TRUE")
#CFA.descriptives <- descriptives.data[429:690, ]
CFA.descriptives<- subset(descriptives.data, IncludedInEFA == "FALSE")

#Separating the EFA and CFA(only items)
sem.data <- data[, 9:56] #EFA & CFA data
sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s

## renaming the column-header
prefix <- "item"
sufix <- c(1:48)
colnam <- paste(prefix,sufix, sep = "" )
colnames(sem.data) <- colnam

### EFA data
EFA.data <- sem.data[1:428, ]
#Polychoric Correlation matrix

correlations <- psych::polychoric(EFA.data, correct = 0)

#Supplementary EFA with Minres Extraction

fa.5F.min.1 <- fa(r=correlations$rho, nfactors = 5, fm= "minres",rotate ="varimax",
                residuals = TRUE, SMC = TRUE, n.obs =428)
EE <- print(fa.5F.min.1, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.min.1 <- dplyr::select(EFA.data ,
                                    -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14))

correlations.red.5F.min.1 <- polychoric(reduced.model.5F.min.1,correct = 0)

fa.5F.min.2 <- fa(r=correlations.red.5F.min.1$rho, nfactors = 5, fm= "minres",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

FF <- print(fa.5F.min.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.min.2 <- dplyr::select(EFA.data, -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14, item34, item47, item21, item13))

correlations.red.5F.min.2 <- polychoric(reduced.model.5F.min.2, correct = 0)

fa.5F.min.3 <- fa(r=correlations.red.5F.min.2$rho, nfactors = 5, fm= "minres",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

GG <- print(fa.5F.min.3, cut = .3, digits = 3, sort = TRUE)

minresTab <- tabledown::fac.tab(fa.5F.min.3, cut =.3,complexity = F)
```

```{r MinResTab}
papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items(Minmum Residual)", note = "Only loading higher than .30 is reported", longtable=T)
```

# Factor analysis with six factors

```{r sixFac, include=F}
# EFA with 6 factor (rejected)

#correlations <- polychoric(EFA.factor, correct = 0)

fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

II <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.1 <- dplyr::select(EFA.data ,
                                    -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23))

correlations.red.6F.1 <- polychoric(reduced.model.6F.1,correct = 0)

fa.6F.2 <- fa(r=correlations.red.6F.1$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

JJ <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.2 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23, item18, item42, item47, item41))

correlations.red.6F.2 <- polychoric(reduced.model.6F.2,correct = 0)

fa.6F.3 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)

KK <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)

# Residuals
residual.6F =residuals(fa.6F.3 , diag = FALSE, na.rm =T)
#Count of numbers of residuals>.05
BigRRR= sum(residual.6F>abs(.05), na.rm =T)
print(BigRRR)

#Total number of off diagonal elements in the data matrix
totRRR = length(reduced.model.6F.2)*(length(reduced.model.6F.2)-1)/2

# Proportion of off-diagonal elements >.10
sumRRR <- sum(BigRRR/totRRR*100)

#hist(residual.6F, main = NULL, xlab = "Six factor Solution: Residuals",ylim=c(0, 400))
#abline(h =65, lwd = 2, lty = 2)
#abline(v =.05,lwd = 2, lty = 2)
sixFac <- tabledown::fac.tab(fa.6F.3, cut =.3,complexity = F)
```

```{r sixFacTab, results='asis'}
papaja::apa_table(sixFac,  caption = "Factor loadings and communality of the retained items(six factor)", note = "Only loading higher than .30 is reported",longtable =T)
```

# Factor Analysis with Unmerged Response Option

```{r DataAppB, include=FALSE}
data <- readRDS("leba_2021-09-08.rds")

#Separating the EFA and CFA(only items)
sem.data <- data[, 9:56] #EFA & CFA data
## renaming the column-header
prefix <- "item"
sufix <- c(1:48)
colnam <- paste(prefix,sufix, sep = "" )
colnames(sem.data) <- colnam
EFA.data <- sem.data[1:428, ]

```

```{r ggplot2AppB, include=F}
apatheme=ggplot2::theme_bw()+
  ggplot2::theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        #text=element_text(family = "Helvetica",),
        legend.title=element_blank(),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'),
        panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
```

```{r EFAassumptionsAppB, include=FALSE}

#KMO test
KMO.1 <- KMO(EFA.data)

# Test of correlation matrix
bartlet.1 <- cortest.bartlett(EFA.data, n =428)

# Univariate normality

#creating normality function
shapiro_test_df <- function(df, bonf= TRUE, alpha= 0.05) {
  l <- lapply(df, shapiro.test)
  s <- do.call("c", lapply(l, "[[", 1))
  p <- do.call("c", lapply(l, "[[", 2))
  if (bonf == TRUE) {
    sig <- ifelse(p > alpha / length(l), "H0", "*")
  } else {
    sig <- ifelse(p > alpha, "H0", "*")
  }
  return(list(statistic= s,
              p.value= p,
              significance= sig,
              method= ifelse(bonf == TRUE, "Shapiro-Wilks test with Bonferroni Correction","Shapiro-Wilks test without Bonferroni Correction")))
}

Shapiro.efa <- shapiro_test_df(EFA.data)

efa.normality.tab = matrix(nrow = 48, ncol = 2)
rownameprefix <- "Item"
rownamesufix <- seq(1:48)
my.item.names <- paste(rownameprefix,rownamesufix, sep = "" )
rownames(efa.normality.tab) <- my.item.names
colnames(efa.normality.tab) <- c("statistic", "p")

efa.normality.tab[,1] <- apa(Shapiro.efa$statistic,2,T)
efa.normality.tab[,2] <- apa(Shapiro.efa$p.value,2,T)

efa.normalityprefix <- efa.normality.tab[,1]
efa.normalitysufix <- Shapiro.efa$significance
efa.normality.stat <- paste(efa.normalityprefix,efa.normalitysufix, sep = "" )

# Multivariate Normality
mardia.1 <- mardia(EFA.data, na.rm = T, plot =F)

# Descriptive Stats
Descriptives <- psych::describe(EFA.data)
alpha <- psych::alpha(EFA.data)
Item.total <- alpha$item.stats

Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), efa.normality.stat,  apa(Item.total$r.cor,2,F))

colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")
rownameprefix <- "Item"
rownamesufix <- seq(1:48)
my.names <- paste(rownameprefix,rownamesufix, sep = "" )
rownames(Des.combined) = (my.names)
```

```{r CorrMatrixAppB, include=FALSE, warning=F,message=F}
#Polychoric Correlation matrix

correlations <- polychoric(EFA.data, correct = 0)
upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]

min.cor.1 <- apa(min(abs(upper)),2,F) #minimum cor.coefficient of the matrix
max.cor.1 <- apa(max(abs(upper)),2,F) # max. correlation coefficient of the matrix

determinets <- det(correlations$rho) 
# Calculating the percentage of correlations higher than .30

BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
totR = length(EFA.data)*(length(EFA.data)-1)/2
cor.per.1 <- print (BigR/totR)*100
```

```{r ParallelEFAAppB, include=FALSE}

# Parallel analysis
Horn <- paran(correlations$rho, iterations=500, centile=0, quietly=FALSE,
           status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
           color=TRUE, col=c("black","red","blue"),
           lty=c(1,2,3), lwd=1, legend=TRUE, 
           width=640, height=640, grdevice=png, seed=0, mat=NA, n=NA)

Adjusted.EV <- data.frame(Horn$AdjEv)
Adjusted.EV$type = c('Adjusted Ev')
Adjusted.EV$num = c(row.names(Adjusted.EV))
Adjusted.EV$num = as.numeric(Adjusted.EV$num)
colnames(Adjusted.EV) = c('eigenvalue', 'type', 'num')

Random.EV <- data.frame(Horn$RndEv)
Random.EV$type = c('Random EV')
Random.EV$num = c(row.names(Random.EV))
Random.EV$num = as.numeric(Random.EV$num)
colnames(Random.EV) = c('eigenvalue', 'type', 'num')

Unadjusted.EV <- data.frame(Horn$Ev)
Unadjusted.EV$type = c('Unadjusted EV')
Unadjusted.EV$num = c(row.names(Unadjusted.EV))
Unadjusted.EV$num = as.numeric(Unadjusted.EV$num)
colnames(Unadjusted.EV) = c('eigenvalue', 'type', 'num')

parallel = ggplot(Adjusted.EV, aes(x=num, y=eigenvalue, shape=type, color=type)) +
  #Add lines connecting data points
  geom_line()+
    geom_line(data = Random.EV) +
  geom_line(data = Unadjusted.EV)+
    #Add the data points.
  geom_point(size=1)+
  geom_point(data = Random.EV, size=1)+
  geom_point(data = Unadjusted.EV, size=1)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
   #Label the x-axis 'Factor Number', and ensure that it ranges from 1-max # of factors, increasing by one with each 'tick' mark.
  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
    #Add vertical line indicating parallel analysis suggested max # of factors to retain
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme

```

```{r ScreePlotAppB, include=FALSE}
Scree <- scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
      hline=NULL,add=F)

FA.Scree <- data.frame(Scree$fv)
FA.Scree$type = c('Factor Analysis')
FA.Scree$num = c(row.names(FA.Scree))
FA.Scree$num = as.numeric(FA.Scree$num)
colnames(FA.Scree) = c('eigenvalue', 'type', 'num')

PA.Scree <- data.frame(Scree$pcv)
PA.Scree$type = c('Principal Component Analysis')
PA.Scree$num = c(row.names(PA.Scree))
PA.Scree$num = as.numeric(PA.Scree$num)
colnames(PA.Scree) = c('eigenvalue', 'type', 'num')

scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
   geom_line()+
  geom_line(data = PA.Scree)+ 
  geom_point(size=1)+
  geom_point(data = PA.Scree, size=1)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme 
```

```{r MAPefaAppB, include=FALSE}
#MAP
psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )
```

Table \@ref(tab:tabDesAppB) summarizes the univariate descriptive statistics for the 48 items with un-merged options. Some of the items were skewed with high Kurtosis values. Our data violated both univariate normality (Shapiro-Wilk statistics) and multivariate normality assumptions [Marida's test]. Multivariate skew was = `r printnum(mardia.1$b1p)` (p <0.001) and multivariate kurtosis was = `r printnum(mardia.1$b2p)` (p <0.001). Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen. Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy. The overall KMO vale for 48 items was `r printnum(KMO.1$MSA)` which was above the cutoff value (.50) indicating a mediocre sample. Bartlett's test of sphericity, $\chi^2$ (`r bartlet.1$df`) = `r apa(bartlet.1$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for the EFA. However only `r apa(cor.per.1, 2,T)`% of the inter-item correlation coefficients were greater than .30. The absolute value of inter-item correlation ranged between `r min.cor.1` to `r max.cor.1`.Figure \@ref(fig:corunm) depicts the correlation matrix. For un-merged response option Horn's parallel analysis with 500 iterations indicated a five-factor solution. However, Scree plot and the MAP method suggested 6-factor solution. five-factor solution . As a result, we tested both five-factor and six-factor solutions. The six factor solution yielded a factor with only two salient loading (Table \@ref(tab:EFAsix). Thus we reject the six factor solution. The five factor solution retained 24 items (Table \@ref(tab:efaunmerged)). However the factors are less interpretable in terms of common theme. Thus we reject the five factor solution.

```{r tabDesAppB, results='asis'}
apa_table(Des.combined, caption = "Descriptive Statistics for Unmerged response options",  note = "*p<.001", longtable =T)
```

```{r corunm, fig.cap="Correlation plot of the items [Unmerged response options]",  out.width="100%"}

ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90 )
#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
#to show pvalue in the fig add p.mat=p.mat
```

```{r facIdFigAppB,  fig.cap='Factor Identification  (A) Parallel analysis (B) Scree Plot [Unmerged response options]', warning=FALSE}
cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")

```

```{r EFAAppB, include=FALSE}
fa.5F.1 <- fa(r=correlations$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
AA <- print(fa.5F.1, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.1 <- dplyr::select(EFA.data ,
                                    -c(item32, item34, item24, item37, item22, item5,
                                        item28, item30, item39,item23, item45, item6, item29, item2, item41))

correlations.red.5F.1 <- polychoric(reduced.model.5F.1,correct = 0)

fa.5F.2 <- fa(r=correlations.red.5F.1$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

BB <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item5,
                                        item28, item30, item39,item23, item45, item6, item29, item2, item41, item46, item13, item15, item25, item1, item26, item14))

correlations.red.5F.2 <- polychoric(reduced.model.5F.2,correct = 0)

fa.5F.3 <- fa(r=correlations.red.5F.2$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )

CC <- print(fa.5F.3, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.3 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item5,
                                        item28, item30, item39,item23, item45, item6, item29, item2, item41, item46, item13, item15, item25, item1, item26, item14, item43, item42))

correlations.red.5F.3 <- polychoric(reduced.model.5F.3,correct = 0)

fa.5F.4 <- fa(r=correlations.red.5F.3$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )

CC <- print(fa.5F.4, cut = .3, digits = 3, sort = TRUE)
```

```{r factordetailsAppB, include=FALSE}
#Preparing the EFA table
efa.table <- tabledown::fac.tab(fa.5F.4,.3, complexity = F) 
```

```{r efaunmerged, results='asis'}
apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
```

```{r EFAAppsix, include=FALSE, warning=F,message=FALSE}
fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
DD <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.1 <- dplyr::select(EFA.data ,
                                    -c(item32, item34, item44,item24, item37, item22, item5,
                                        item28,item39,item23, item45, item6, item29, item2, item41, item30))

correlations.red.6F.2 <- polychoric(reduced.model.6F.1,correct = 0)

fa.6F.2 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

EE <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)
reduced.model.6F.2 <- dplyr::select(EFA.data ,
                                    -c(item32, item34, item44,item24, item37, item22, item5,
                                        item28,item39,item23, item45, item6, item29, item2, item41, item30, item46, item36,item1, item25))
correlations.red.6F.3 <- polychoric(reduced.model.6F.2,correct = 0)
fa.6F.3 <- fa(r=correlations.red.6F.3$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
FF <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.3 <- dplyr::select(EFA.data ,
                                    -c(item32, item34, item44,item24, item37, item22, item5,
                                        item28,item39,item23, item45, item6, item29, item2, item41, item30, item46, item36,item1, item25, item18))
correlations.red.6F.4 <- polychoric(reduced.model.6F.3,correct = 0)
fa.6F.4 <- fa(r=correlations.red.6F.4$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
FF <- print(fa.6F.4, cut = .3, digits = 3, sort = TRUE)

efa.table.2 <- tabledown::fac.tab(fa.6F.4,.3, complexity = F) 
```

```{r EFAsix, results='asis'}
apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
```

# Items Retained in the Five Factor Solution [Unmerged Responses]

| **Five Factor Solution [Unmerged Responses] (24 Items)** |
|---------------------------------------------------------|
| **F1**                                                  |
| `r label(sem.data$item19)`                              |
| `r label(sem.data$item20)`                              |
| `r label(sem.data$item18)`                              |
| `r label(sem.data$item21)`                              |
| `r label(sem.data$item4)`                               |
| **F2**                                                  |
| `r label(sem.data$item11)`                              |
| `r label(sem.data$item10)`                              |
| `r label(sem.data$item12)`                              |
| `r label(sem.data$item8)`                               |
| `r label(sem.data$item7)`                               |
| `r label(sem.data$item9)`                               |
| **F3**                                                  |
| `r label(sem.data$item3)`                               |
| `r label(sem.data$item27)`                              |
| `r label(sem.data$item40)`                              |
| **F4**                                                  |
| `r label(sem.data$item35)`                              |
| `r label(sem.data$item48)`                              |
| `r label(sem.data$item33)`                              |
| `r label(sem.data$item47)`                              |
| `r label(sem.data$item44)`                              |
| `r label(sem.data$item31)`                              |
| `r label(sem.data$item38)`                              |
| **F5**                                                  |
| `r label(sem.data$item16)`                              |
| `r label(sem.data$item17)`                              |
| `r label(sem.data$item36)`                              |

```{r EFAResidualsAppB, eval=FALSE, fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE, include=FALSE, results='asis'}
hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
abline(h =35, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)
```

# Geographic Locations of Survey Participants
```{r Timezone-tab, include=FALSE, warning=F,message=FALSE}
descriptives.data%>%
  tbl_summary(
    label = slypos_demographics_tz.factor ~ "Time zone - Country",
    statistic = list(all_categorical() ~ "{n} ({p}%)"),
    missing = "no",
    sort = all_categorical() ~ "frequency",
    include = "slypos_demographics_tz.factor"
  )  %>% bold_labels() %>% 
  modify_header(label ~ "") %>%
  modify_caption("Geographical Location") -> tz_table

  as_tibble(tz_table, format = 'pipe') -> tz_tibble

as_kable(tz_table, format = "latex",booktabs = T, longtable =T) -> tz_kable

```

```{r tztabprint, results='asis'}

tz_kable %>% 
  kable_styling(latex_options = c("repeat_header")) %>% 
  column_spec(1,width = "10cm") %>% 
  column_spec(2,width = "2cm")

```

>>>>

```{r factormp, warning=F}
map <- readr::read_csv("Table_raw/map_stat")
map <- map[,-1]
papaja::apa_table(map,align = "c", caption = "MAP Statistics",  font_size = "small")
```

@@

### 2022-01-02 appendix-2.Rmd
Duplicate chunk error fixed

---
title             : "Supplementary"
shorttitle        : "SA"

author: 
  - name          : "Mushfiqul Anwar Siraji"
    affiliation   : "1, *"
    email         : "mushfiqul.anwarsiraji@monash.edu"
    role:         
      - Formal Analysis
      - Visualization
      - Writing – original draft
      - Writing – review & editing;

  - name          : "Rafael Robert Lazar"
    affiliation   : "2, 3, *"
    role:
      - Data curation
      - Investigation
      - Project administration
      - Visualization
      - Writing – original draft
      - Writing – review & editing;

  - name          : "Juliëtte	van Duijnhoven"
    affiliation   : "4"
    email         : "j.v.duijnhoven1@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

  - name          : "Luc Schlangen"
    affiliation   : "5"
    email         : "l.j.m.schlangen@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

  - name          : "Shamsul Haque"
    affiliation   : "1"
    email         : "shamsul@monash.edu"
    role:         
      - Conceptualization
      - Supervision
      - Writing – review & editing

  - name          : "Vineetha Kalavally"
    affiliation   : "6"
    email         : "vineetha@monash.edu"
    role:         
      - Supervision
      - Writing – review & editing

  - name          : "Céline Vetter"
    affiliation   : "7, 8"
    email         : "celine.vetter@colorado.edu"
    role:         
      - Conceptualization
      - Writing – review & editing

  - name          : "Gena Glickman"
    affiliation   : "9"
    email         : "gena.glickman@usuhs.edu"
    role:         
      - Conceptualization
      - Methodology
      - Writing – review & editing

  - name          : "Karin Smolders"
    affiliation   : "10"
    email         : "k.c.h.j.smolders@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Writing – review & editing

  - name          : "Manuel Spitschan"
    corresponding : yes
    affiliation   : "11, 2, 3"
    email         : "manuel.spitschan@psy.ox.ac.uk"
    role:         
      - Conceptualization
      - Data curation
      - Investigation
      - Project administration
      - Visualization
      - Methodology
      - Writing – original draft
      - Writing – review & editing

affiliation:
  - id            : "1"
    institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
  - id            : "2"
    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
  - id            : "3"
    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
  - id            : "4"
    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
  - id            : "5"
    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Intelligent Lighting Institute, Eindhoven, Netherlands"
  - id            : "6"
    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Malaysia, Selangor, Malaysia"
  - id            : "7"
    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
  - id            : "8"
    institution   : "Ximes GmbH, Frankfurt, Germany"
  - id            : "9"
    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
  - id            : "10"
    institution   : "Eindhoven University of Technology, Human-Technology Interaction Group, Eindhoven, Netherlands"
  - id            : "11"
    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, UK"
  - id            : "*"
    institution   : "Joint first author"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    latex_engine: xelatex
    includes:
      in_header: header.tex

mainfont: Arial
---

```{r options, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
set.seed(123)
par(family = "Arial")
```

```{r lib, include=FALSE}

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(car)#revercoding 
library(psych)
library(dlookr)
library(plyr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
library(gt)
library(gtExtras)
library(likert)
library(VIM) #Missing data
library(kutils)
library(simsem)
library(tabledown)
library(Hmisc)
r_refs("references.bib")
```

# SA: Confirming the five factor solution obtained using minimum residual extraction method

@@

```{r EFATableAppB, results='asis'}
apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
```

```{r EFAAppsix, include=FALSE, warning=F,message=FALSE}
fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
DD <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)

>>>>

@@

```{r efaunmerged, results='asis'}
apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
```

```{r EFAAppsix, include=FALSE, warning=F,message=FALSE}

library(Hmisc)
fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
DD <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)

### 2022-01-02 manuscript.Rmd
Duplicate chunk error fixed

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    latex_engine: xelatex
    includes:
      in_header: header.tex
appendix:
  - "appendix-1.Rmd"
  - "appendix-2.Rmd"
mainfont: Arial
---

@@

Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution. Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution. However, the minimum average partial (MAP) method (Table \@ref(tab:Map-stat1)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.

@@

Lastly, we developed a short-LEBA (n=23) using IRT analysis. We fitted a graded response model model to the combined EFA and CFA sample ( n =`r nrow(data)`). We discarded 5 items with relatively flat item information curve [I($\theta$) <.20]. IRT analysis indicated short form of LEBA is a psychometrically sound measure. Item fit indexes and person fit index for all five fitted model were acceptable. Items had diverse slope parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behavior. Test information curve also indicated a good coverage of underlying trait continuum with precision.

@@

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('appendix-1.Rmd')
```

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('appendix-2.Rmd')
```

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    keep_tex: false
    latex_engine: xelatex
    includes:
      in_header: header.tex
appendix:
  - "appendix-1.Rmd"
  - "appendix-2.Rmd"
  - "appendix-3.Rmd"
mainfont: Arial
---

@@

Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution. Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution. However, the minimum average partial (MAP) method (Table \@ref(tab:factormp)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.

@@

Lastly, we developed a short-LEBA (n=23) using IRT analysis. We fitted a graded response model model to the combined EFA and CFA sample (n =`r nrow(data)`). We discarded 5 items with relatively flat item information curve [I($\theta$) <.20]. IRT analysis indicated short form of LEBA is a psychometrically sound measure. Item fit indexes and person fit index for all five fitted model were acceptable. Items had diverse slope parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behavior. Test information curve also indicated a good coverage of underlying trait continuum with precision.

@@
